\section*{Abstract}

    In the European Union, the public sector is one of the most open-data intensive sectors. The re-use of open data can contribute, for example, to the growth of the European economy, the development of artificial intelligence and overcoming societal challenges.

	Given the increasing importance of data standards for the EU institutions, a number of initiatives driven by the public sector, industry and academia have been kick-started in recent years. Some have grown organically, while others are the result of standardisation work. The vocabularies and semantics that they are introducing, together with the technologies that they are using, all differ. These differences hamper data interoperability and thus its reuse by them or by the wider public. This creates the need for a common data standard for publishing public reference data and models, hence allowing data from different sources to be easily accessed, linked, and consequently reused.
	
	The Public Sector Information (PSI) directive across the EU calls for open, unobstructed access to public data in order to improve transparency and to boost innovation via the reuse of public data. The reference data maintained and published by the Publications Office Office of the European Union (OP) has been identified as data with a high-reuse potential. Therefore, making this data available in machine-readable formats, as well as following the data as a service paradigm, are required in order to maximise its reuse.
	
	In this context, the Publications Office of the European Union maintains and publishes an ever-increasing number of reference data assets which are vital in the context of inter-institutional information exchange, access, retrievability and re-use of information. With regards to reference data, the PO provides an ever-increasing number of services to the main institutional stakeholders and with the aim to extend them to a broader public, enabling active or passive participation in the reference data life cycle, standardisation and harmonisation.
	
	This document provides a working definition of the architectural stance and design decisions that are to be adopted for the asset publication life-cycle process. This process is materialised as the publication workflow and is currently employed by the Standardisation Unit (SU) at the Publications Office of the European Union (OP).
	
% 	In this document we (a) establish the baseline architecture, supported by  strategic and motivational information; and (b) develop a target architecture guiding the digital transformation processes towards new technologies. This constitutes a natural evolution in response to changing mission needs defined by SU management, and also takes into consideration the strategic directions proposed by the PO, the European Commission (EC) and the European Parliament (EP) as presented below.